---
title: Directory manipulation with R
author: Anthony Chau
date: '2020-06-09'
slug: directories-manipulation-R
categories:
  - R
tags:
  - reproducible research
---

Quick note about directories with base R. 

# Check if a directory exists

We use the **dir.exists()** function. **dir.exists()** takes as input, a path to a directory, specified as a character string. You can also specify multiple paths in a single character vector. The function will return a boolean indicating if the directory exists.  
```{r, eval = FALSE}

dir.exists("path/to/dir")

# can specific multiple paths

dir_paths <- c("path/to/dir1", "path/to/dir2")

dir.exists(dir_paths)


```


# Create a directory.

We use the **dir.create()** function. **dir.create()** takes as input, a path to a direcotyr specified as a character string. We cannot supply multiple character vectors to  **dir.create()**.
```{r, eval = FALSE}

# create a new directory in the current directory
dir.create("new_dir")

# create a new sub-directory in the new_dir
dir.create("new_dir/sub_dir")

# doesnt' work
dir.create(c("new-dir1", "new-dir2"))
```

